---
title: "Flight path processing"
author: "Francisko de Moraes Rezende"
date: ""
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Setup

### Loading and installing packages in case it is necessary

```{r}
list_of_packages <- c("tidyverse", "plotly", "shiny", "here", "fs")
new_packages <-
  list_of_packages[!(list_of_packages %in% installed.packages()[, "Package"])]
if (length(new_packages))
  install.packages(new_packages)
```


```{r}
library(tidyverse)
library(plotly)
library(shiny)
library(here)
library(fs)
```

### Defining the function I used to calculate distance

```{r}
calc_flight_dist <- name <- function(dat) {
  dat_dist <-  {{dat}} %>% 
  dplyr::filter(!is.na(x_1)) %>%
  dist() %>% 
  as.matrix()

return(sum((dat_dist[row(dat_dist) == col(dat_dist) + 1])))
  
}
```

### Defining function I used to calculate all variables from flight trajectory

```{r}
calc_flight_trajectory_vars <- function(dat) {
  
dat %>% 
  group_by(butterfly_flight) %>% 
  summarise(flight_dist = calc_flight_dist(.),
            min_x = min(.$x_1, na.rm = T),
            max_x = max(.$x_1, na.rm = T),
            min_y = min(.$y_1, na.rm = T),
            max_y = max(.$y_1, na.rm = T),
            min_z = min(.$z_1, na.rm = T),
            max_z = max(.$z_1, na.rm = T))
}

```

### Defining the function I used to make the 3d plots

```{r}
plots_flight_path <- function(dat) {
  
plot_ly(data = dat,
        type = "scatter3d", 
        x = dat$x_1 ,
        y = dat$y_1,
        z = dat$z_1,
        mode = "lines")
}

```


## Processing the CSV files

### Creats the dataframe that will receive the data from the flight paths

```{r}
flights <-
tibble::tibble(
  butterfly_flight = character(),
  flight_dist = numeric(),
  min_x = numeric(),
  max_x = numeric(),
  min_y = numeric(),
  max_y = numeric(),
  min_z = numeric(),
  max_z = numeric()
) 
```

### b195 t1

#### Reads the data

```{r}
b195_t1 <- readr::read_csv(here::here("unpaired-points", "b195-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t1") 
```

#### Calculates the variables

```{r}
flights <- 
  calc_flight_trajectory_vars(b195_t1) %>% 
  dplyr::bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t1)
```


### b195 t2

#### Reads the data

```{r}
b195_t2 <- readr::read_csv(here::here("unpaired-points", "b195-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t2)
```


### b195 t3

#### Reads the data

```{r}
b195_t3 <- readr::read_csv(here::here("unpaired-points", "b195-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t3)
```

### b195 t4

#### Reads the data

```{r}
b195_t4 <- readr::read_csv(here::here("unpaired-points", "b195-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t4) %>%
  bind_rows(flights, .)
```

```{r}
flights
```


#### Plots the trajectory

```{r}
plots_flight_path(b195_t4)
```


### b195 t5

#### Reads the data

```{r}
b195_t5 <- readr::read_csv(here::here("unpaired-points", "b195-t5-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t5") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t5) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t5)
```


### b206 t1

#### Reads the data

```{r}
b206_t1 <- readr::read_csv(here::here("unpaired-points", "b206-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b206-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b206_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b206_t1)
```

```{r}
flights
```

