---
title: "Flight path processing"
author: "Francisko de Moraes Rezende"
date: ""
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

The code for generating this document lives [here](https://github.com/francisko-rezende/flight-path-experiment), in the file `index.Rmd`.

## Setup

### Loading and installing packages in case it is necessary

```{r}
list_of_packages <- c("tidyverse", "plotly", "shiny", "here", "DT")
new_packages <-
  list_of_packages[!(list_of_packages %in% installed.packages()[, "Package"])]
if (length(new_packages))
  install.packages(new_packages)
```


```{r}
library(tidyverse)
library(plotly)
library(shiny)
library(here)
library(DT)
```

### Defining the function I used to calculate distance

```{r}
calc_flight_dist <- name <- function(dat) {
  dat_dist <-  {{dat}} %>% 
  dplyr::filter(!is.na(x_1)) %>%
  dist() %>% 
  as.matrix()

return(sum((dat_dist[row(dat_dist) == col(dat_dist) + 1])))
  
}
```

### Defining function I used to calculate all variables from flight trajectory

```{r}
calc_flight_trajectory_vars <- function(dat) {
  
dat %>% 
  group_by(butterfly_flight) %>% 
  summarise(flight_dist = calc_flight_dist(.),
            min_x = min(.$x_1, na.rm = T),
            max_x = max(.$x_1, na.rm = T),
            min_y = min(.$y_1, na.rm = T),
            max_y = max(.$y_1, na.rm = T),
            min_z = min(.$z_1, na.rm = T),
            max_z = max(.$z_1, na.rm = T))
}

```

### Defining the function I used to make the 3d plots

```{r}
plots_flight_path <- function(dat) {
  
plot_ly(data = dat,
        type = "scatter3d", 
        x = dat$x_1 ,
        y = dat$y_1,
        z = dat$z_1,
        mode = "lines")
}

```


## Processing the CSV files

### Creates the dataframe that will receive the data from the flight paths

```{r}
flights <-
tibble::tibble(
  butterfly_flight = character(),
  flight_dist = numeric(),
  min_x = numeric(),
  max_x = numeric(),
  min_y = numeric(),
  max_y = numeric(),
  min_z = numeric(),
  max_z = numeric()
) 
```

### b195 t1

#### Reads the data

```{r}
b195_t1 <- readr::read_csv(here::here("unpaired-points", "b195-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t1") 
```

#### Calculates the variables

```{r}
flights <- 
  calc_flight_trajectory_vars(b195_t1) %>% 
  dplyr::bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t1)
```


### b195 t2

#### Reads the data

```{r}
b195_t2 <- readr::read_csv(here::here("unpaired-points", "b195-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t2)
```


### b195 t3

#### Reads the data

```{r}
b195_t3 <- readr::read_csv(here::here("unpaired-points", "b195-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t3)
```

### b195 t4

#### Reads the data

```{r}
b195_t4 <- readr::read_csv(here::here("unpaired-points", "b195-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t4) %>%
  bind_rows(flights, .)
```

```{r}
flights
```


#### Plots the trajectory

```{r}
plots_flight_path(b195_t4)
```


### b195 t5

#### Reads the data

```{r}
b195_t5 <- readr::read_csv(here::here("unpaired-points", "b195-t5-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b195_t5") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b195_t5) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b195_t5)
```


### b206 t1

#### Reads the data

```{r}
b206_t1 <- readr::read_csv(here::here("unpaired-points", "b206-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b206-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b206_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b206_t1)
```

### b206 t2

#### Reads the data

```{r}
b206_t2 <- readr::read_csv(here::here("unpaired-points", "b206-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b206-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b206_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b206_t2)
```

### b206 t3

#### Reads the data

```{r}
b206_t3 <- readr::read_csv(here::here("unpaired-points", "b206-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b206-t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b206_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b206_t3)
```

### b206 t4

#### Reads the data

```{r}
b206_t4 <- readr::read_csv(here::here("unpaired-points", "b206-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b206-t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b206_t4) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b206_t4)
```

### b211 t1

#### Reads the data

```{r}
b211_t1 <- readr::read_csv(here::here("unpaired-points", "b211-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b211-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b211_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b211_t1)
```

### b211 t2

#### Reads the data

```{r}
b211_t2 <- readr::read_csv(here::here("unpaired-points", "b211-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b211-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b211_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b211_t2)
```

### b211 t3

#### Reads the data

```{r}
b211_t3 <- readr::read_csv(here::here("unpaired-points", "b211-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b211-t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b211_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b211_t3)
```

### b211 t4

#### Reads the data

```{r}
b211_t4 <- readr::read_csv(here::here("unpaired-points", "b211-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b211-t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b211_t4) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b211_t4)
```

### b216 t1

#### Reads the data

```{r}
b216_t1 <- readr::read_csv(here::here("unpaired-points", "b216-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b216-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b216_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b216_t1)
```

### b216 t2

#### Reads the data

```{r}
b216_t2 <- readr::read_csv(here::here("unpaired-points", "b216-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b216-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b216_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b216_t2)
```

### b216 t4

#### Reads the data

```{r}
b216_t4 <- readr::read_csv(here::here("unpaired-points", "b216-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b216-t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b216_t4) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b216_t4)
```

### b220 t2

#### Reads the data

```{r}
b220_t2 <- readr::read_csv(here::here("unpaired-points", "b220-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b220-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b220_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b220_t2)
```

### b220 t3

#### Reads the data

```{r}
b220_t3 <- readr::read_csv(here::here("unpaired-points", "b220-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b220-t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b220_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b220_t3)
```

### b228 t1

#### Reads the data

```{r}
b228_t1 <- readr::read_csv(here::here("unpaired-points", "b228-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t1)
```

### b228 t2

#### Reads the data

```{r}
b228_t2 <- readr::read_csv(here::here("unpaired-points", "b228-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t2)
```

### b228 t3

#### Reads the data

```{r}
b228_t3 <- readr::read_csv(here::here("unpaired-points", "b228-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t3)
```

### b228 t4

#### Reads the data

```{r}
b228_t4 <- readr::read_csv(here::here("unpaired-points", "b228-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t4) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t4)
```

### b228 t5

#### Reads the data

```{r}
b228_t5 <- readr::read_csv(here::here("unpaired-points", "b228-t5-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t5") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t5) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t5)
```

### b228 t6

#### Reads the data

```{r}
b228_t6 <- readr::read_csv(here::here("unpaired-points", "b228-t6-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t6") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t6) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t6)
```

### b228 t7

#### Reads the data

```{r}
b228_t7 <- readr::read_csv(here::here("unpaired-points", "b228-t7-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b228-t7") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b228_t7) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b228_t7)
```

### b238 t1

#### Reads the data

```{r}
b238_t1 <- readr::read_csv(here::here("unpaired-points", "b238-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238-t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t1)
```

### b238 t2

#### Reads the data

```{r}
b238_t2 <- readr::read_csv(here::here("unpaired-points", "b238-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238-t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t2)
```

### b238 t4

#### Reads the data

```{r}
b238_t4 <- readr::read_csv(here::here("unpaired-points", "b238-t4-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238-t4") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t4) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t4)
```

### b238 t5

#### Reads the data

```{r}
b238_t5 <- readr::read_csv(here::here("unpaired-points", "b238-t5-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238-t5") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t5) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t5)
```

### b224 t2

#### Reads the data

```{r}
b224_t2 <- readr::read_csv(here::here("unpaired-points", "b224-t2-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b224_t2") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b224_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b224_t2)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b224_t2) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b224_t2)
```

### b224 t3

#### Reads the data

```{r}
b224_t3 <- readr::read_csv(here::here("unpaired-points", "b224-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b224_t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b224_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b224_t3)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b224_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b224_t3)
```

### b238 t3

#### Reads the data

```{r}
b238_t3 <- readr::read_csv(here::here("unpaired-points", "b238-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238_t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t3)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t3)
```

### b238 t6

#### Reads the data

```{r}
b238_t6 <- readr::read_csv(here::here("unpaired-points", "b238-t6-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b238_t6") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t6) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t6)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b238_t6) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b238_t6)
```

### b246 t1

#### Reads the data

```{r}
b246_t1 <- readr::read_csv(here::here("unpaired-points", "b246-t1-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b246_t1") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b246_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b246_t1)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b246_t1) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b246_t1)
```

### b246 t3

#### Reads the data

```{r}
b246_t3 <- readr::read_csv(here::here("unpaired-points", "b246-t3-unpaired-points-xyz.csv")) %>% 
  dplyr::mutate(butterfly_flight = "b246_t3") 
```

#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b246_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b246_t3)
```


#### Calculates the variables

```{r}
flights <-
  calc_flight_trajectory_vars(b246_t3) %>%
  bind_rows(flights, .)
```

#### Plots the trajectory

```{r}
plots_flight_path(b246_t3)
```

 
## Table with all the data

### Making the separator in `butterfly_flight` homogenous and renaming it to `butterfly_take`

```{r}
flights %>% 
  tidyr::separate(col = butterfly_flight, into = c("butterfly", "flight"), sep = "([-_])") %>% 
  tidyr::unite("butterfly_take", butterfly:flight, sep = "_") -> flights
```

### Printing the actual table

```{r}
flights %>% 
  DT::datatable(extensions = 'Buttons',
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All"))))
```

