---
title: "Testing map for auto distance calculation"
author: "Francisko de Moraes Rezende"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loads and installs packages used if needed

```{r warning=FALSE}
list_of_packages <- c("tidyverse", "here", "fs", "plotly")
new_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages)

library(tidyverse)
library(here)
library(fs)
library(plotly)
```

# Loads files

The following chunk loads all .csv files in the "subset-unpaired-points" folder
and puts

```{r warning=FALSE, message=FALSE}
files <- fs::dir_ls(here::here("subset-unpaired-points"))

files %>% 
  purrr::map_dfr(readr::read_csv, .id = "source") -> all_flights
```

## trying to auto load all files

```{r}
fs::dir_ls(here::here('wand'), recurse = T, regexp = "unpaired-points-xyz.csv$") %>% 
  purrr::map_dfr(readr::read_csv, .id = "source") -> all_flights

all_flights %>% 
  dplyr::distinct(source)
```


# Defines functions

```{r}
calc_flight_dist <- function(dat) {
  dat_dist <-  {{dat}} %>% 
  dplyr::filter(!is.na(x_1)) %>%  # removes NA
  dist() %>%  # calculates distance
  as.matrix()  # converts it to a matrix

return(sum((dat_dist[row(dat_dist) == col(dat_dist) + 1])))  # sums the distance between points by summing the points in line n and column n + 1
  
}
```

```{r}
plots_flight_path <- function(dat) {
  
plotly::plot_ly(data = dat,
        type = "scatter3d", 
        x = dat$x_1 ,
        y = dat$y_1,
        z = dat$z_1,
        mode = "lines")
}
```

```{r}
calc_straight_dist <- function(dat) {
  
dist_dat <- 
  dat %>% 
  dplyr::filter(!is.na(x_1)) %>%
  dist() %>% 
  as.matrix()

return(dist_dat[1, nrow(dist_dat)])  
}

```


```{r}
all_flights %>%
  dplyr::group_by(source) %>%
  tidyr::nest() %>% 
  dplyr::mutate(distance = purrr::map_dbl(data, ~ calc_flight_dist(.x)),
                straight_distance = purrr::map_dbl(data, ~ calc_straight_dist(.x)),
                sinuosity = distance / straight_distance,
                plot_3d = purrr::map(data, ~ plots_flight_path(.x)),
                butterfly = stringr::str_extract(source, pattern = "b\\d{3}"),
                take = stringr::str_extract(source, pattern = "t\\d{1}")) 
# -> processed
```

```{r}
string <-  "/home/francisko/coding/r/flight-path-experiment/subset-unpaired-points/b195-t1-unpaired-points-xyz.csv"

str_extract(string, pattern = "b\\d{3}")

str_extract(string, pattern = "t\\d{1}")
```


```{r}
read_csv(here("subset-unpaired-points", "b211-t2-unpaired-points-xyz.csv")) %>% 
  calc_flight_dist()
```

```{r}
read_csv(here("subset-unpaired-points", "b211-t2-unpaired-points-xyz.csv")) %>% 
  calc_straight_dist()
```


```{r}
read_csv(here("subset-unpaired-points", "b195-t1-unpaired-points-xyz.csv")) %>% 
  calc_flight_dist()
```


Calculates how many rows there are after removing NaNs, might be useful to calculate speed.

```{r}
read_csv(here("subset-unpaired-points", "b211-t2-unpaired-points-xyz.csv")) %>% 
  tibble::rowid_to_column(var = "row_number") %>% 
  tidyr::drop_na() %>% 
  nrow()
```

The above might not work because of gaps in the tracking, the method below might be better

Gotta take the difference between the min and max values so we know the full extent of the flight even though some points might be missing.

```{r}
read_csv(here::here("subset-unpaired-points", "b211-t2-unpaired-points-xyz.csv")) %>% 
  tibble::rowid_to_column(var = "row_number") %>% 
  tidyr::drop_na() %>%
  select(row_number) %>% 
  range()
```